% Created 2021-06-01 Tue 13:55
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Bruce Graham}
\date{\today}
\title{Resume}
\hypersetup{
 pdfauthor={Bruce Graham},
 pdftitle={Resume},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\maketitle



\section{CONTACT}
\label{sec:org59e6c9b}

Cell: 0027 72 091 6687   IP telephone: 0027 87 550 7192    Email: bruceg72@protonmail.ch

\section{SUMMARY}
\label{sec:org06a3921}

Bruce is a BSc graduate through UNISA. 
Bruce has been an ardent Open Source Unix enthusiast and hobbyist since Linus Torvalds announced his kernel. 
Bruce has tinkered with device drivers on FreeBSD in C, set up his own PostgreSql server and built clusters, as well as building his own systems.
Bruce has developed expertise in Bash and R and has programmed in SQL, C and Python.


\section{TRAITS}
\label{sec:orga29cb17}

\begin{itemize}
\item Excellent written communicator
\item Expert problem solver on Linux
\item Technically orientated and
\item An independent worker (with facilities for remote work.)
\end{itemize}

\section{SKILLS}
\label{sec:orgf72eb31}

\begin{center}
\begin{tabular}{ll}
Skill & Level\\
\hline
R & senior\\
Python & intermediate\\
Ansible & beginner\\
deb & working\\
rpm & working\\
Git & working\\
Bash & working\\
Command line & expert\\
Ubuntu & senior\\
CentOS & senior\\
PostgreSQL & intermediate\\
C & senior\\
Apache config & intermediate\\
Shiny & beginner/inter\\
 & \\
\hline
\end{tabular}
\end{center}


\section{PROJECTS}
\label{sec:orgd9b469b}

\begin{itemize}
\item Bruce compiled the 2.18 kernel tweaking the device drivers and fitting the available drivers. On numerous occassions Bruce compiled a full monolithic kernel and successfully ran his machine.
\item Bruce constructed his own Linux systems, researching required hardware and available drivers.
\item Bruce installed a picoITX form factor PC using a 12V DC ATX power supply in his caravan.
\item Bruce tweaked the FreeBSD USB driver to pick up his USB device which had an unknown IC and an unusual signature.
\item Bruce used lithographic principles to build his own hand made circuit board.
\item Bruce conducted a 'from scratch' analysis of his expenses in R, attempting to incorporate work from his actuarial studies on ruin theory.
\item Bruce made various attempts at creating an insightful Dashboard for his portfolio of equities.
\end{itemize}

\section{EDUCATION}
\label{sec:org105f627}

Honours Bachelor of Science (Incomplete)		\textit{[2005-01-31 Mon] } to \textit{[2006-11-30 Thu]}
Operational Research
University of South Africa, Pretoria

Bachelor of Science					\textit{[1993-01-31 Sun] } to \textit{[2004-10-31 Sun]}
Operational Research, Mathematics, Statistics (2:2)
University of South Africa, Pretoria

\section{WORK EXPERIENCE}
\label{sec:orgf90b887}

Personal investment manager				     2017-01 to present
Work from home
Bruce conducts research and reading on the markets and economy with an eye to harnessing ultra long term market forces and trends. Bruce has become a connoisseur of investment products with excellent risk management and is not a return chaser.

Entrepreneur   		                             2008-04 to 2015-07
Wilfredo’s Ice Cream Company
Bruce performed product R\&D and established a factory. He also researched a ﬁnancial reporting system and performed the bookkeeping. With his business partner, they produced ice cream and delivered it. Bruce administered the business and guided the direction of the business, spending his free time building a spreadsheet model to anticipate cashflow and profitability of the business.

Entrepreneur  		                             2006-09 to 2008-01
Karoo Wireless
Bruce was involved in the pilot phase of this business. He scoured the surrounding mountains for antennae sights. He lobbied the municipality for support. He canvassed the area for customers and lobbied for business. Bruce formed a partnership with a company in George to perform the technical setup. Bruce left after having secured the first few customers.



\section{REFERENCES}
\label{sec:org6f2303b}

On request
\end{document}